### 2024-10-23 Article/Graph_sections/Eq_Graphs.tex
minori

In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.

@@

	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{id_{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{id_{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{id_{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{id_{Z'}}& Z_2 \ar[d]_{id_{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{id_{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	If we show that $g$ is an isomorphism we are done. Consider the cubes
	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{F_j(b)} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
	in which the vertical faces are pullbacks. Since the bottom face is a stable pushout we can deduce that
	\[\xymatrix{Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{z_2} & Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{u_2}\\ Z_1 \ar[r]_{z_1}& W & Z_1 \ar[r]_{u_1}& U }\]
	are pushout squares too. The arrow $g$ fits in the following  diagram
	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
	and thus it is an isomorphism.
\end{proof}

@@

Let now $(z_1, z_2, z_3)\colon (A'_2, B'_2, C'_2)\to (E, F, G, e, f, g)$ and $(w_1, w_2, w_3)\colon (A'_3, B'_3, C'_3)\to (E, F, G, e, f, g)$ be two morphisms such that 
\[(z_1, z_2, z_3)\circ (h'_1, h'_2, h'_3)=(w_1, w_2, w_3)\circ (k'_1, k'_2, k'_3)\] 
Let $z\colon B'_4\to F$ be the arrow induced by $z_2$ and $w_2$, we want to construct the dotted arrow $w\colon C'_4 \to G$ in the diagram below

 \todo{Finisci il diagramma}
\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[rr]^{p'_2} && B'_4  \ar[rr]^{z}&& F \ar[ddddd]^{g}\\& C'_1 \ar[d]_{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \\ C'_3 \ar[dd]_{m_3}\\&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C'_4 \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]

>>>>

\iffalse 
In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.

@@

	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{id_{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{id_{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{id_{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{id_{Z'}}& Z_2 \ar[d]_{id_{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{id_{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	If we show that $g$ is an isomorphism we are done. Consider the cubes
	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{F_j(b)} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
	in which the vertical faces are pullbacks. Since the bottom face is a stable pushout we can deduce that
	\[\xymatrix{Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{z_2} & Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{u_2}\\ Z_1 \ar[r]_{z_1}& W & Z_1 \ar[r]_{u_1}& U }\]
	are pushout squares too. The arrow $g$ fits in the following  diagram
	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
	and thus it is an isomorphism.
\end{proof} 
\fi

@@

Let now $(z_1, z_2, z_3)\colon (A'_2, B'_2, C'_2)\to (E, F, G, e, f, g)$ and $(w_1, w_2, w_3)\colon (A'_3, B'_3, C'_3)\to (E, F, G, e, f, g)$ be two morphisms such that 
\[(z_1, z_2, z_3)\circ (h'_1, h'_2, h'_3)=(w_1, w_2, w_3)\circ (k'_1, k'_2, k'_3)\] 
Let $z\colon B'_4\to F$ be the arrow induced by $z_2$ and $w_2$, we want to construct the dotted arrow $v\colon C'_4 \to G$ in the diagram below

 \todo{Sistema il diagramma mettendo gli opportuni buchi}
\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[dd]|(.5)\hole_(.62){q'_1}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[ddd]|(.33)\hole^{q'_2} \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[ddd]_{q'_3} \ar[rr]^(.65){p'_2} && B'_4  \ar[rr]^(.65){z}&& F \ar[ddddd]^{g}\\& C'_1 \ar@/^.2cm/[drr]^{h'_3} \ar@/_.2cm/[ddl]_{k'_3} \ar[d]^{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \ar@/^.2cm/[dddr]^{z_3} \ar[lddd]_{t'_3}\\ C'_3 \ar@/_.5cm/[ddrr]^(.65){p'_3} \ar[ddrrrr]_{w_3} \ar[dd]_{m_3}\\&T\ar[dd]|(.25)\hole|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]|(.25)\hole_{w} && U \ar[dd]^(.3){u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]_(.65){y_1} & & C'_4 \ar@{.>}[rr]_(.65){v} \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
